Re-Allocation of Resources during Releases \titlenote{Copyright note}

### 2013-11-28 paper1/paper1.tex
updated paper for result on rq3,4,5(partial), written new scripts

\renewcommand{\labelenumi}{Q\theenumi:}
\begin{enumerate}
\item What is the release process used by the project? \newline
We will be giving a qualitative description of Linux Kernel development in brief to give anser to this question.
\item How many developers are allocated troughout different segments of a release period? What significant difference can be observed between the segments of an entire release period? \newline
Answer to this question will give us a big picture of Linux Kernel development community as well as the contrubution of developers in different periods within a stable release period. We will calculate Jaccard Distance to differentiate the behavior of developers during RTR and normal development period.
\item Do developers work on different areas of the system around the time of release? \newline
We want to see if developers are looking at different types of files in the code-base around the time of release which is being considered as the merge period or merge window\cite{linux_kernel}. We are expecting this would be the RTR are in a release time where technical debt may be introduced.
\item Do developers mostly work on their own codes around the system?
Many developers are working on many files. We will find out which files has been churned mostly by which developer so that we can understand how developers are distributed among the system.
\item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)? \newline
To answer this question we will look into the frequency of file churns made into files. Difference or distance of the files between normal development period and the RTR period or merge period of a release.
\end{enumerate}

@@

\subsubsection{DA in RD Period}
As like MP we can extract the RDP from the releases. RDP here in Linux Kernel development process is being considered as from the date of RC1 release (i.e.\ first release candidate opening the gate for the development of the next release) to the next release (major, minor or micro) date. For example if the date of release for ``linuxv2.6.13-rc1'' after releasing ``linuxv2.6.12'' is 2005-06-29 and date of publishing the next release ``linuxv2.6.13'' is 2005-08-28 then we are calling this 60 days of development period for the release as the RDP. Table 4 is showing some development periods of different releases.

@@

\subsection{Developers' contributions around the time of release}
\textit{Do developers work on different areas of the system around the time of release?}\newline
\textit{Do developers mostly work on their own codes around the system?}

@@

If we compare the percentage of working in owned files ($\omega$\textit{P}) in merge period and the percentage of working in owned files in general ($\Omega$\textit{P}) for the life time for each developer works in the merge period then we see a very significant difference as shown in figure 9.
\begin{figure}
\begin{center}
\includegraphics[height=1.7in,width=3in]{ownedFilesMPRDPBox.png}
\caption{\small \sl Percentage of working in owned files during Merge Period and the that of life time}
\end{center}
\end{figure}
We still interested to see the correlation of $\omega$\textit{P} with $\Omega$\textit{P} to get more idea about the role of merge period over the role in general for any other time in release development. Figure 10 plots the graphical representation of the correlation.
\begin{figure}
\begin{center}
\includegraphics[height=1.7in,width=3in]{owPercentMPRDPCorr.png}
\caption{\small \sl X axis: \% of working in owned files during Merge Period, Y axis: \%of working in owned files during Release Development Period}
\end{center}
\end{figure}
As we find the residual standard error is 33.69 on 8055 degrees of freedom  and the multiple R-squared value is 0.04803, Adjusted R-squared value is 0.04791. We found the F-statistic 406.4 and the p-value is < 2.2e-16.

If we add other independent variables ``churn frequency in merge period (\c{c}\textit{F})'', ``churn frequency in general (\c{C}\textit{F})'' and ``average ownership for the life time ($\omega$\textit{Avg})'' then the correlation looks like as shown in figure 11.

So, finally we can say that in merge periods developers work on more native codes while during the regular release development period the percentage of working with native code is very less in number.

@@

\section{Acknowledgments}
... ... ...
\bibliographystyle{abbrv}
\bibliography{paper1} 
\appendix
%Appendix A
\section{Headings in Appendices}
Apendix section will be written later with the following subsections may be:
\subsection{Introduction}
...
\subsection{Background and Motivation}
\subsubsection{Related Works}
...
\subsubsection{Methodology and Data}
...
\subsection{Conclusions}
...
\subsection{Acknowledgments}
...

>>>>

\renewcommand{\labelenumi}{Q\theenumi:}
\begin{enumerate}
\item What is the release process used by the project? \newline
We will be giving a qualitative description of Linux Kernel development in brief to give anser to this question.
\item How many developers are allocated troughout different segments of a release period? What significant difference can be observed between the segments of an entire release period? \newline
Answer to this question will give us a big picture of Linux Kernel development community as well as the contrubution of developers in different periods within a stable release period. We will calculate Jaccard Distance to differentiate the behavior of developers during RTR and normal development period.
\item Do developers work on different areas of the system around the time of release? \newline
We want to see if developers are looking at different types of files in the code-base around the time of release which is being considered as the merge period or merge window\cite{linux_kernel}. We are expecting this would be the RTR are in a release time where technical debt may be introduced.
\item Do developers work in others' code in a high proportion during the rush period?
Many developers are working on many files. We will find out which files has been churned mostly by which developer so that we can understand how developers are distributed among the system.
\item Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)? \newline
To answer this question we will look into the frequency of file churns made into files. Difference or distance of the files between normal development period and the RTR period or merge period of a release.
\end{enumerate}

@@

\subsubsection{DA in Release Development Period}
As like MP we can extract the RDP from the releases. RDP here in Linux Kernel development process is being considered as from the date of RC1 release (i.e.\ first release candidate opening the gate for the development of the next release) to the next release (major, minor or micro) date. For example if the date of release for ``linuxv2.6.13-rc1'' after releasing ``linuxv2.6.12'' is 2005-06-29 and date of publishing the next release ``linuxv2.6.13'' is 2005-08-28 then we are calling this 60 days of development period for the release as the RDP. Table 4 is showing some development periods of different releases.

@@

\subsection{Developers' contributions around the time of release}
\textit{Do developers work on different areas of the system around the time of release?}\newline
\textit{Do developers work in others' code in a high proportion during the rush period?}

@@

If we compare the percentage of working in owned files ($\omega$\textit{P}) in merge period and the percentage of working in owned files in general ($\Omega$\textit{P}) for the life time for each developer works in the merge period then we see a significant difference as shown in figure 9.
\begin{figure}
\begin{center}
\includegraphics[height=1.7in,width=3in]{ownedFilesMPRDPBox.png}
\caption{\small \sl Percentage of working in owned files during Merge Period and the that of life time}
\end{center}
\end{figure}

Now, to predict if developers work in others' code in a high proportion during the rush period we would like to observe the correlation of the \% of working in owned files in merge period with other independent variables ``churn percentage in merge period (\c{c}\textit{P})'', ``churn percentage in general (\c{C}\textit{P})'', ``average ownership ($\omega$\textit{Avg})'' and \% of wirking in owned files in general ($\Omega$\textit{P}). Table 6 shows the Spearman rank correlation among the \% of working with owned files and other variables. We can see there is no statistically significant positive relationship between the measures and the \% of working in owned files

All three correlations Kendall, Pearson and Spearman calculates that the percentage of working with owned files doesn't to any other variables strongly as we predicted seeing figure 7 having a very poor percentage of contribution (19.82\%) on owned files during the merge period of time. But we can see a significant strong relation between the \% of churn in general and \% of churn in merge period which is 0.7199 according to Kendall, 0.7028 according to Pearson and 0.8446 according to Spearman. Also the correlation between the \% of churn in general and the average ownership is strong according to Spearman model which is 0.7982. We are giving the priority to Spearman model because Spearman correlation is a more robust correlation technique \cite{nagappan_defect}.
If we consider the following models with our variables:
\renewcommand{\labelenumi}{M\theenumi:}
\begin{enumerate}
\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}}
\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}, $\omega$\textit{Avg}}
\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}, $\omega$\textit{Avg}, \c{c}\textit{P}}
\item{Predictors: ($\omega$\textit{P}), $\Omega$\textit{P}, $\omega$\textit{Avg}, \c{c}\textit{P}, \c{C}\textit{P}}
\end{enumerate}
then we see the linear regression model for the \% of working with owned code measure using all the predictors has an R-squared value 0.1132 with residual standard error is 32.52 on 8053 degrees of freedom, Adjusted R-squared value is 0.1139. F-statistic is 342.8 and the p-value is < 2.2e-16. R-square is a measure of variance in the dependent variable that is accounted for by the model built using the predictors \cite{nagappan_defect}. R-square is a measure of the fit for the given data set. It cannot be interpreted as the quality of the dataset to make future predictions.

\begin{table}[ht]
\caption{Cross Correlations}  % title of Table
\centering 						% used for centering table
\begin{tabular}{c c c c c c}			% centered columns (6 columns)
\hline\hline						%inserts double horizontal lines
% table heading
Measures  & $\omega$\textit{P} & $\Omega$\textit{P} & $\omega$\textit{Avg} & \c{c}\textit{P} & \c{C}\textit{P} \\ [0.5ex]
\hline 							% single horizontal line
% inserting body of the table
$\omega$\textit{P}		& 1.0000	& 0.2897	& 0.4496	& 0.3325	& 0.2826 \\
$\Omega$\textit{P}	& --			& 1.0000	& 0.7110	& 0.3979	& 0.5075 \\
$\omega$\textit{Avg}	& --			& --			& 1.0000 	& 0.6754 	& \textbf{0.7982} \\
\c{c}\textit{P}			& -- 			& -- 		 	& --			& 1.0000	& \textbf{0.8446} \\
\c{C}\textit{P}			& -- 			& -- 			& -- 			& -			& 1.0000 \\
[1ex]							% adds vertical space
\hline 							% inserts single line
\end{tabular}
\label{table:nonlin} 				% is used to refer this table in the text
\end{table}

So, finally we can say that in merge periods developers work in more native codes while during the regular release development period the percentage of working with native code is very low in number although this percentage of working in owned code during merge period does not significantly relate to other co-factors.

\subsection{Developers' focus on code-base around the time of release}
\textit{Are there certain areas of the system that receive increased attention (i.e.\ do developers focus on a smaller set of files around releases)?}
Answer to the following questions are going to be looked for to answer this research question:
\renewcommand{\labelenumi}{q\theenumi:}
\begin{enumerate}
\item{How many times a file has been committed during merge period?}
\item{How many authors made those commits?}
\item{How many churns were made to the files during each commit?}
\item{What is the time interval for the commits for a file?}
\item{How many files each developer deals with during merge period?}
\item{How many files each developer deals with during release development period?}
\item{What is the jaccard distance J(mp1, rdp1), J(rdp1, rdp0) and J(rdp0, mp1)?}
\end{enumerate}
We found the relation J(mp1, rdp1) > J(rdp1, rdp0) < J(rdp0, mp1) for the minor releases is significant but among the micro stable releases this relation is not significant at all.

@@

\bibliographystyle{abbrv}
\bibliography{paper1} 
\appendix
%Appendix A
\section{Headings in Appendices}
Apendix section will be written later with the following subsections may be:
\subsection{Introduction}
...
\subsection{Background and Motivation}
\subsubsection{Related Works}
...
\subsubsection{Methodology and Data}
...
\subsection{Conclusions}
...
\subsection{Acknowledgments}
...
